\Large Inferential Analysis of the Supreme Court Citation Network

### 2018-03-23 Tex/paper.tex
added ToDos, updated chapter 5

In what follows we develop a theoretical case that citations on the US Supreme Court are characterized by forms of complex dependence that are common in networks. We then develop an extension of a model---the exponential random graph model---that can incorporate both exogenous covariates and complex forms of interdependence into a directed dyadic analysis of citations. Finally, we develop and estimate a specification of this model in an analysis of US Supreme Court citations between 1937 and 2001. We find robust support for the inherent complexity underpinning the formation of citation ties, and show that incorporating complex dependence into the model of citation formation significantly improves the model's predictive performance.

@@

We include two sets of dummy variables that account for the issue areas of cases. In one set of dummy variable---sender intercepts---the variable $X_{ij}$ indicates the issue area of the sending case ($i$). In the set of receiver intercepts $X_{ij}$ indicates the issue are of the receiver case. Issue area data comes from the Supreme Court Database (SCDB) \citep{spaeth2014supreme}. We include these variables because \citet{cross2010determinants} find that the number of citations to Supreme Court opinions depends heavily on the issue area of the case.

@@

\begin{itemize}
\item mention new variable: overruled cases
\end{itemize}

%%%% DONT DELETE THESE COMMENTS, INCLUDE IDEAS FOR ADDITIONAL COVARIATES %%%%%

@@

\begin{table}[H]
\centering
\begin{tabular}{rllll}
\hline \hline
 & mean & range & mean & range \\ 
  \hline
precision & 0.5872 & (0.5781, 0.5962) & 0.8622 & (0.8593, 0.8668) \\ 
  recall & 0.0565 & (0.0547, 0.0587) & 0.5839 & (0.5777, 0.592) \\ 
  F1 score & 0.103 & (0.1, 0.1069) & 0.6963 & (0.6915, 0.7027) \\ 
   \hline \hline
\end{tabular}
\caption{The predictive performance of the directed dyadic models with no trends, over ten 80/20 train/test splits.}
\label{tab:prediction_linear}
\begin{tabular}{rllll}
\hline \hline
 & mean & range & mean & range \\ 
  \hline
precision & 0.5589 & (0.5508, 0.5757) & 0.8677 & (0.865, 0.8718) \\ 
  recall & 0.098 & (0.0943, 0.103) & 0.5943 & (0.5887, 0.6032) \\ 
  F1 score & 0.1667 & (0.1618, 0.1748) & 0.7054 & (0.7013, 0.7119) \\ 
   \hline \hline
\end{tabular}
\caption{The predictive performance of the directed dyadic models with linear trends, over ten 80/20 train/test splits.}
\label{tab:prediction_linear}
\begin{tabular}{rllll}
\hline \hline
 & mean & range & mean & range \\ 
  \hline
precision & 0.6441 & (0.6302, 0.6536) & 0.8671 & (0.8626, 0.873) \\ 
  recall & 0.0852 & (0.0832, 0.0863) & 0.594 & (0.5874, 0.6012) \\ 
  F1 score & 0.1504 & (0.1473, 0.1525) & 0.705 & (0.7008, 0.712) \\ 
   \hline \hline
\end{tabular}
\caption{The predictive performance of the directed dyadic models with quadratic trends, over ten 80/20 train/test splits.}
\label{tab:prediction_quadratic}
\begin{tabular}{rllll}
\hline \hline
 & mean & range & mean & range \\ 
  \hline
precision & 0.642 & (0.6311, 0.6527) & 0.8664 & (0.8645, 0.8681) \\ 
  recall & 0.0866 & (0.0835, 0.0882) & 0.5947 & (0.591, 0.5978) \\ 
  F1 score & 0.1526 & (0.1475, 0.1552) & 0.7053 & (0.7026, 0.7079) \\ 
   \hline \hline
\end{tabular}
\caption{The predictive performance of the directed dyadic models with cubic trends, over ten 80/20 train/test splits.}
\label{tab:prediction_cubic}
\begin{tabular}{rllll}
\hline \hline
 & mean & range & mean & range \\ 
  \hline
precision & 0.645 & (0.635, 0.6668) & 0.8681 & (0.8639, 0.8712) \\ 
  recall & 0.0864 & (0.083, 0.0887) & 0.5955 & (0.5899, 0.6004) \\ 
  F1 score & 0.1524 & (0.1468, 0.1562) & 0.7064 & (0.7018, 0.7094) \\ 
   \hline \hline
\end{tabular}
\caption{The predictive performance of the directed dyadic models with quartic trends, over ten 80/20 train/test splits.}
\label{tab:prediction_quartic}
\end{table}

@@

>>>>

In what follows we develop a theoretical case that citations on the US Supreme Court are characterized by forms of complex dependence that are common in networks. We then develop an extension of a model---the exponential random graph model---that can incorporate both exogenous covariates and complex forms of interdependence into a directed dyadic analysis of citations. Finally, we develop and estimate a specification of this model in an analysis of US Supreme Court citations between 1937 and 2001. We find robust support for the inherent complexity underpinning the formation of citation ties, and show that incorporating complex dependence into the model of citation formation significantly improves the model's predictive performance.\\[0.5cm]
\textit{Comment from Benjamin Kassov: I think the discussion in the introduction of the paper focusing on a "case-based" versus network based analysis is a bit short. 
I was left slightly confused by what a "case-based" analysis of citation actually is or what it means. 
I can see several different conceptions of this, some being more problematic than others in a methodological sense, 
although none of them are ideal for analyzing networks and all likely suffer some amount of OV bias.}

@@

We include two sets of dummy variables that account for the issue areas of cases. In one set of dummy variable---sender intercepts---the variable $X_{ij}$ indicates the issue area of the sending case ($i$). In the set of receiver intercepts $X_{ij}$ indicates the issue are of the receiver case. Issue area data comes from the Supreme Court Database (SCDB) \citep{spaeth2014supreme}. We include these variables because \citet{cross2010determinants} find that the number of citations to Supreme Court opinions depends heavily on the issue area of the case. Table \ref{issue_area_coding} states which number represents which issie area.

\begin{table}[]
\centering
\begin{tabular}{llll}
1 & Criminal Procedure & 8  & Economic Activity    \\
2 & Civil Rights       & 9  & Judicial Power       \\
3 & First Amendment    & 10 & Federalism           \\
4 & Due Process        & 11 & Interstate Relations \\
5 & Privacy            & 12 & Federal Taxation     \\
6 & Attorneys          & 13 & Miscellaneous        \\
7 & Unions             & 14 & Private Action      
\end{tabular}
\caption{Code Book for the variable \textit{Issue Area}. This information originates from the Supreme Court Database code book.}
\label{issue_area_coding}
\end{table}

@@

\begin{itemize}
\item ToDo: mention new variable: overruled cases
\end{itemize}

\textit{Comment from Benjamin Kassow: In section 5, I think the discussion is mostly good, but could be organized a bit differently. 
I think the discussion of the random intercepts is a bit confusing early on (it is explained more effectively later). }
%%%% DONT DELETE THESE COMMENTS, INCLUDE IDEAS FOR ADDITIONAL COVARIATES %%%%%

@@

\begin{table}[H]
\centering
\begin{tabular}{rllll}
\hline \hline
 & mean & range & mean & range \\ 
  \hline
precision & 0.5872 & (0.5781, 0.5962) & 0.8622 & (0.8593, 0.8668) \\ 
  recall & 0.0565 & (0.0547, 0.0587) & 0.5839 & (0.5777, 0.592) \\ 
  F1 score & 0.103 & (0.1, 0.1069) & 0.6963 & (0.6915, 0.7027) \\ 
   \hline \hline
\end{tabular}
\caption{The predictive performance of the directed dyadic models with no trends, over ten 80/20 train/test splits.}
\label{tab:prediction_linear}
\begin{tabular}{rllll}
\hline \hline
 & mean & range & mean & range \\ 
  \hline
precision & 0.5589 & (0.5508, 0.5757) & 0.8677 & (0.865, 0.8718) \\ 
  recall & 0.098 & (0.0943, 0.103) & 0.5943 & (0.5887, 0.6032) \\ 
  F1 score & 0.1667 & (0.1618, 0.1748) & 0.7054 & (0.7013, 0.7119) \\ 
   \hline \hline
\end{tabular}
\caption{The predictive performance of the directed dyadic models with linear trends, over ten 80/20 train/test splits.}
\label{tab:prediction_linear}
\begin{tabular}{rllll}
\hline \hline
 & mean & range & mean & range \\ 
  \hline
precision & 0.6441 & (0.6302, 0.6536) & 0.8671 & (0.8626, 0.873) \\ 
  recall & 0.0852 & (0.0832, 0.0863) & 0.594 & (0.5874, 0.6012) \\ 
  F1 score & 0.1504 & (0.1473, 0.1525) & 0.705 & (0.7008, 0.712) \\ 
   \hline \hline
\end{tabular}
\caption{The predictive performance of the directed dyadic models with quadratic trends, over ten 80/20 train/test splits.}
\label{tab:prediction_quadratic}
\end{table}

@@

\textit{Comment from Benjamin Kassow: In section 6.2 (predictive performance), I like what is here, but was hoping to see a bit more discussion about the predictive 
performance of the model, with some explanation of what the predictive performance means. 
I understand it (I think), but depending on where this gets sent to, I am not sure if all reviewers will. 
I also think tying this into the overall model explanation or discussion of model performance overall will be helpful for better 
integrating this section into the rest of the manuscript.}
